---
title: "Setting the Partner Countries List with Substantial GNI Figures."
author: "ambijat"
date: "02/07/2020"
output:
  md_document:
    variant: markdown_github
---

## Creating a Partner List

The partners of trade are the variables in column each country that has entered into trade with the reporting country. There almost 200 countries in the world. But, each is not significant enough to be enlisted for its trade value. Therefore, some criteria needs to be set up for selecting the range of column variables. And, here we can choose **GNI**, the Gross National Income as the criterion for eliminating the countries whose trade is assumed to non-significant.

```{r, echo=TRUE, include=FALSE}
library(dplyr)
library(tidyverse)
```
#### WDI - World Development Indicators library
It is suitable for downloading the data for individual countries from the world bank database.
```{r, include=TRUE}
library(WDI)
WDIsearch("gni.*current")
```
If you the name then "GNI (current US$)" is of relevance to us. We take its indicator which is "NY.GNP.MKTP.CD" to find and import the GNI figures for all the countries.
```{r, echo=TRUE, include=TRUE}
indicator <- "NY.GNP.MKTP.CD"
wdi_cat <- WDI(indicator = indicator, start = 2010, end = 2010, extra = T)
wdi_cat[1:10,]
```
As you can see a sample of 10 rows where the country codes and GNI figures ("NY.GNP.MKTP.CD" column) are given is presented. And, we will be needing only the some of these columns for our data processing.

```{r, include=TRUE}
names(wdi_cat)
wdi2 <- wdi_cat %>%
  select("country", "NY.GNP.MKTP.CD", "iso3c")
head(wdi2)
```
So, there are 3 columns for our need, 
1. country, 
2. NY.GNP.MKTP.CD, 
3. iso3c. 

The last one is the country code that is necessary for joining the dataframe with our partners list we have.

Loading country_list from excel file downloaded from the UN Comtrade database.

https://unstats.un.org/unsd/tradekb/Knowledgebase/50377/Comtrade-Country-Code-and-Name

```{r, include=TRUE}
library(readxl)
country_list <- read_excel("comtradecountry_nowlist.xlsx")
```
renaming the columns of the dataframe
```{r, include=TRUE}
colnames(country_list) <- c("country.code", "country.name", "iso3c")
head(country_list)
```
The WDI data is joined with the country_list so as to match the GNI for UN Comtrade list countries.
```{r, include=TRUE}
pp <- left_join(country_list, wdi2, by = "iso3c")
colnames(pp)[5] <- "GNI"
names(pp)
```
After joining the datasets the share of each country's GNI against the world GNI is calculated. A new column share is created for enlisting the ratios of each country's GNI.
```{r, include=TRUE}
pp$share <- round((pp$GNI/6.594123e+13)*100, 2)
head(pp)
```
removing NA rows by using complete.cases
```{r, include=TRUE}
pp1 <- na.omit(pp)
nrow(pp)
nrow(pp1)
```
As you can see the complete cases are only 191 out of total cases of 248. Now filtering only those countries whose GNI share is above 0.
```{r, include=TRUE}
pp2 <- pp1 %>%
  filter(share > 0) %>%
  select(country.code, country.name)
nrow(pp2)
```
The list of countries whose GNI is of some significance are 156 in total. So, for the panel data the list of 156 countries would be used for creating a block of matrix against the selected commodities. It would allow us only meaningful entities for datadownloading.
```{r, eval=FALSE, include=TRUE}
write.csv(pp2, "partner_list.csv", row.names = F)
```
Above command shall export the list of 156 country.name and their country.code in a comma separated file (csv).