---
title: "Setting the Partner Countries List with Substantial GNI Figures."
author: "ambijat"
date: "02/07/2020"
output: html_document
---

## Partner List

The partners of trade are the variables in column each country that has entered into trade with the reporting country. There almost 200 countries in the world. But, each is not significant enough to be enlisted for its trade value. Therefore, some criteria needs to be set up for selecting the range of column variables. And, here we can choose **GNI**, the Gross National Income as the criterion for eliminating the countries whose trade is assumed to non-significant.

```{r, echo=TRUE, include=FALSE}
library(dplyr)
library(tidyverse)
```
#### WDI - World Development Indicators library
It is suitable for downloading the data for individual countries from the world bank database.
```{r, include=TRUE}
library(WDI)
WDIsearch("gni.*current")
```
If you the name then "GNI (current US$)" is of relevance to us. We take its indicator which is "NY.GNP.MKTP.CD" to find and import the GNI figures for all the countries.
```{r, echo=TRUE, include=TRUE}
indicator <- "NY.GNP.MKTP.CD"
wdi_cat <- WDI(indicator = indicator, start = 2010, end = 2010, extra = T)
wdi_cat[1:10,]
```
As you can see a sample of 10 rows where the country codes and GNI figures ("NY.GNP.MKTP.CD" column) are given is presented. And, we will be needing only the some of these columns for our data processing.

```{r, include=TRUE}
names(wdi_cat)
wdi2 <- wdi_cat %>%
  select("country", "NY.GNP.MKTP.CD", "iso3c")
head(wdi2)
```
So, there are 3 columns for our need, 1. country, 2. NY.GNP.MKTP.CD, 3. iso3c. The last one is the country code that is necessary for joining the dataframe with our partners list we have.


