---
title: "Classification Template for S4 at AG5 Level"
output: 
  md_document:
    variant: markdown_github
---

## For Classification
The JSON file for S4 classification can be downloaded from https://comtrade.un.org/Data/cache/classificationS4.json.
This has all the AG levels upto 5. We need to extract the AG5 level from this file.

Reading the JSON file with the help of library rjson. We use the unlist method to flatten the data and convert it into dataframe.
```{r include=TRUE}
library(rjson)
string <- "classificationS4.json"
reporters <- fromJSON(file=string)

df <- lapply(reporters, function(results)
{
  data.frame(matrix(unlist(results), ncol=3, byrow=T))
})
sapply(df, class)
```
## Extracting the AG5 level.
Now you have df as a list of data frames. We will collapse it into one single dataframe.
We have also need a bit dressing of the new dataframe such as removing the top 2 rows and then re numbering the rows.
```{r, include=TRUE}
df <- do.call(rbind, df)
df <- df[-(1:2),] 
rownames(df) <- 1:nrow(df)
```
We can see the first column X1 contains the number codes for various commodity levels. It has all the levels out of which we can extract those commodities which have 5 digit code, meaning the AG 5 level. This can be done as follows.

If you see the condition nchar(df$X1) == 5 mentioned as row condition against all the columns, it is the one that will give us all the commodities for desired level. If you need AG4 level then change it from 5 to 4. 
```{r, include=TRUE}
df1 <- df[nchar(df$X1) == 5, ]
```
The next step below is for a tricky situation in S4 classification. There are several Memorandum Items, which are yet to be classified and hence are under single categories. I have removed these Memorandum Items which have letter X against each code.
```{r, include=TRUE}
df2 <- df1[!grepl("X",df1$X1), ]
```
After this we can select the relevant first 2 columns and rename them and renumber them as below.
```{r, include=TRUE}
df4 <- subset(df2, select = c("X1", "X2"))
colnames(df4) <- c("Commodity.code", "Commodity.name")
rownames(df4) <- 1:nrow(df4)
head(df4)

```
## Joining Partner COuntries with S4AG5 Commodity level.
First initializing the libraries.
```{r, eval=FALSE, include=TRUE}
library(dplyr)
library(tidyverse)
```
Next, we import the partner countries from partner_list. 
```{r, include=TRUE}
pd <- read.csv("partner_list.csv", stringsAsFactors = F)
colnames(pd) <- c("Partner.Code", "Partner.name")
```
# combining partner list and s4
```{r, include=TRUE}
sa <- merge(df4, pd)
colnames(sa) <- c("Commodity.code", "Commodity.name", "Partner.Code", "Partner.name")
nrow(sa)
```
## Selecting a group of Commodities
If we look into the total rows of dataframe, then the number is quite large 4,13,868 (which is 2653*156). This is usually problematic for the UN Comtrade data limitation for a guest user is 1,00,000 queries. Therefore, it is advisable to work for desired group of commodities. 

